### 2018-08-25 Sections/costs_and_attributes_in_quantum_networks.tex
Added quantum voting, enigma machines
Started 2 col figs

\begin{figure}[htpb]
\includegraphics[width=0.3\textwidth]{data_proc_ineq}
\caption{A sequence of events \mbox{$X\to Y\to Z$}. The data processing inequality states that the mutual information from beginning to end is upper-bounded by the mutual information between neighbouring stages, as per Eq.~(\ref{eq:data_proc_ineq}).}\label{fig:data_proc_ineq}	
\end{figure}

@@

A dephasing channel can be easily converted to a distance metric as follows. First we reparameterise the dephasing channel into,
\begin{align}
\mathcal{E}(\hat\rho) &= p\hat\rho + (1-p)\hat{Z}\hat\rho\hat{Z}\nonumber\\
&= (2p-1)\hat\rho + (1-p)(\hat{Z}\hat\rho\hat{Z} + \hat\rho).	
\end{align}
Now \mbox{$2p-1$} is the probability that the state is not dephased and \mbox{$1-p$} is the probability that the state is replaced with the completely dephased state. Therefore the probability of multiple applications of the channel not dephasing the state scales multiplicitavely as,
\begin{align}
p_\mathrm{no\, error} = \prod_{i}(2p_i-1),
\end{align}
which is additive in a logarithmic scale as before,
\begin{align}
\log(p_\mathrm{no\, error}) = \sum_i \log(2p_i-1),
\end{align}
which acts as a distance metric. This approach can similarly be applied to other Pauli channels.

>>>>

\begin{figure}[!htbp]
\includegraphics[width=0.3\textwidth]{data_proc_ineq}
\caption{A sequence of events \mbox{$X\to Y\to Z$}. The data processing inequality states that the mutual information from beginning to end is upper-bounded by the mutual information between neighbouring stages, as per Eq.~(\ref{eq:data_proc_ineq}).}\label{fig:data_proc_ineq}	
\end{figure}

@@

A dephasing channel can be easily converted to a distance metric as follows. First we reparameterise the dephasing channel into,
\begin{align}
\mathcal{E}(\hat\rho) &= p\hat\rho + (1-p)\hat{Z}\hat\rho\hat{Z}\nonumber\\
&= (2p-1)\hat\rho + (1-p)(\hat{Z}\hat\rho\hat{Z} + \hat\rho).	
\end{align}
Now \mbox{$2p-1$} is the probability that the state is not dephased and \mbox{$1-p$} is the probability that the state is replaced with the completely dephased state. Therefore the probability of multiple applications of the channel not dephasing the state scales multiplicitavely as\footnote{With this parameterisation, in the limit of many applications of the dephasing channel, an input state asymptotes to the completely dephased state, \mbox{$\lim_{n\to\infty} \mathcal{E}^n(\hat\rho) = \frac{1}{2}(\hat{Z}\hat\rho\hat{Z}+\hat\rho)$}. Thus, \mbox{$2p-1$} can be regarded as a discretised parameterisation of a system's $T_2$-time\index{$T_2$-time}.},
\begin{align}
p_\mathrm{no\, error} = \prod_{i}(2p_i-1),
\end{align}
which is additive in a logarithmic scale as before,
\begin{align}
\log(p_\mathrm{no\, error}) = \sum_i \log(2p_i-1),
\end{align}
which acts as a distance metric. This approach can similarly be applied to other Pauli channels.

### 2018-08-25 Sections/cryptowars.tex
Started 2 col figs

\dropcap{B}{efore} describing any specific cryptographic protocols, let us define what is meant by `security' in a cryptographic context. We differentiate between \textit{information theoretic security}\index{Information-theoretic security}, as opposed to \textit{computational security}\index{Computational security}.

In the former, the laws of quantum information bound the amount of information that can be extracted from a system, irrespective of measurement or computational operations. Thus, such security can be regarded as attack-independent.

In the latter, security is based on the assumption that an adversary's computational resources are insufficient to perform cryptanalysis or brute-force cracking. Clearly the former makes a far stronger statement about the security of a protocol than the latter.

@@

Thankfully, there are two saving graces. First of all, much research is being carried out into \textit{post-quantum classical cryptography}\index{Post-quantum classical cryptography}. That is, public-key cryptosystems based upon trapdoor functions\index{One-way functions} that reside outside of \textbf{BQP} and are therefore not efficiently attacked by quantum computers. One such line of research is to construct cryptosystems based upon \textbf{NP}-complete problems, such as the McEliece protocol\index{McEliece protocol}. Recall from Fig.~\ref{fig:complexity_classes} that \textbf{NP}-complete is strongly believed to reside completely outside of \textbf{BQP}. However, while many computer scientists might be comfortable with such a level of security, it is nonetheless based on the unproven conjecture that \textbf{NP}-complete and \textbf{BQP} do not intersect, i.e \mbox{$\mathbf{NP}\nsubseteq\mathbf{BQP}$}. What would be much more satisfying would be protocols demonstrating information-theoretic security\index{Information-theoretic security} rather than computational security\index{Computational security}. Here quantum mechanics can help us -- \textit{quantum cryptography}.

@@

In Sec.~\ref{sec:state_of_the_art} we summarise the state-of-the-art in the physical implementation of QKD.

@@

\begin{figure*}[!htbp]
\includegraphics[width=0.8\textwidth]{QAB}
\caption{Protocol for quantum anonymous broadcasting. (a) A central trusted server prepares GHZ states and distributes them amongst a group of users, one qubit per user. All users measure in the $\pm$-basis. (b) All users classically broadcast their measurement outcomes yielding shared random parity. During broadcast, the broadcaster lies about his measurement outcome to flip the joint parity if he wishes to transmit `1', or tells the truth to transmit `0'. The joint parity encodes the message of the anonymous user, which all listeners are able to recover. Importantly, only one user may broadcast at a time, otherwise the recovered message will be given by the XOR of all the simultaneously broadcast messages.} \label{fig:QAB}
\end{figure*}

>>>>

\dropcap{B}{efore} describing any specific cryptographic protocols, let us define what is meant by `security' in a cryptographic context. We differentiate between \textit{information theoretic security}\index{Information-theoretic security}, as opposed to \textit{computational security}\index{Computational security}:

\begin{itemize}
	\item Information-theoretic security: the laws of quantum information bound the amount of information that can be extracted from a system, irrespective of measurement or computational operations. Thus, such security can be regarded as attack-independent.
	\item Computational security: is based on the assumption that an adversary's computational resources are insufficient to perform cryptanalysis or brute-force cracking. Clearly the former makes a far stronger statement about the security of a protocol than the latter.
\end{itemize}

@@

Thankfully, there are two saving graces. First of all, much research is being carried out into \textit{post-quantum classical cryptography}\index{Post-quantum classical cryptography}. That is, public-key cryptosystems based upon trapdoor functions\index{One-way functions} that reside outside of \textbf{BQP} and are therefore not efficiently attacked by quantum computers. One such line of research is to construct cryptosystems based upon \textbf{NP}-complete problems, such as the McEliece protocol\index{McEliece protocol} \cite{bib:McEliece}. Recall from Fig.~\ref{fig:complexity_classes} that \textbf{NP}-complete is strongly believed to reside completely outside of \textbf{BQP}. However, while many computer scientists might be comfortable with such a level of security, it is nonetheless based on the unproven conjecture that \textbf{NP}-complete and \textbf{BQP} do not intersect, i.e \mbox{$\mathbf{NP}\nsubseteq\mathbf{BQP}$}. What would be much more satisfying would be protocols demonstrating information-theoretic security\index{Information-theoretic security} rather than computational security\index{Computational security}. Here quantum mechanics can help us -- \textit{quantum cryptography}.

@@

@@

\if 2\pubmode
\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{QAB_long}
\caption{Protocol for quantum anonymous broadcasting. (a) A central trusted server prepares GHZ states and distributes them amongst a group of users, one qubit per user. All users measure in the $\pm$-basis. (b) All users classically broadcast their measurement outcomes yielding shared random parity. During broadcast, the broadcaster lies about his measurement outcome to flip the joint parity if he wishes to transmit `1', or tells the truth to transmit `0'. The joint parity encodes the message of the anonymous user, which all listeners are able to recover. Importantly, only one user may broadcast at a time, otherwise the recovered message will be given by the XOR of all the simultaneously broadcast messages.} \label{fig:QAB}
\end{figure}
\else
\begin{figure*}[!htbp]
\includegraphics[width=0.8\textwidth]{QAB}
\caption{Protocol for quantum anonymous broadcasting. (a) A central trusted server prepares GHZ states and distributes them amongst a group of users, one qubit per user. All users measure in the $\pm$-basis. (b) All users classically broadcast their measurement outcomes yielding shared random parity. During broadcast, the broadcaster lies about his measurement outcome to flip the joint parity if he wishes to transmit `1', or tells the truth to transmit `0'. The joint parity encodes the message of the anonymous user, which all listeners are able to recover. Importantly, only one user may broadcast at a time, otherwise the recovered message will be given by the XOR of all the simultaneously broadcast messages.} \label{fig:QAB}
\end{figure*}
\fi

### 2018-08-25 Sections/entanglement_the_ultimate_quantum_resource.tex
Fixed up telescopy
Added quantum voting, enigma machines
Started 2 col figs

Foremost, Bell pairs (Sec.~\ref{sec:bell_state_res}) -- the simplest entangled states -- are an utterly indispensable resource for countless quantum protocols. In brief, Bell pairs find applicability in, amongst many others, the following key protocols:
\begin{itemize}
\item Cluster states (Sec.~\ref{sec:CSQC})\index{Cluster states}: a Bell pair is also a 2-qubit cluster state, a supply of which can be employed in fusion strategies to prepare larger cluster states, enabling universal, distributed MBQC.
\item Quantum state teleportation (Sec.~\ref{sec:teleport})\index{Quantum state teleportation}: a shared Bell pair between Alice and Bob forms the elementary quantum resource upon which the state teleportation protocol is constructed.
\item QKD (Sec.~\ref{sec:QKD})\index{Quantum key distribution (QKD)}: the E91 QKD\index{E91 protocol} protocol is built upon a reliable stream of distributed Bell pairs, enabling private communication with perfect information theoretic security.
\item Modularised quantum computation (Sec.~\ref{sec:module})\index{Modularised quantum computation}: using Bell pairs, entanglement swapping (Sec.~\ref{sec:swapping})\index{Entanglement swapping} can be employed to fuse neighbouring, but potentially distant modules together using operations local to each module.
\item Superdense coding (Sec.~\ref{sec:superdense})\index{Superdense coding}: a shared Bell pair enables the communication of two classical bits of information via transmission of a single qubit, thereby doubling classical channel capacity\index{Channel capacity}.
\end{itemize}

@@

So which ought our quantum hubs specialise in, entanglement distribution, entangling measurements, or both? For most practical purposes the former is far more powerful and robust. Let us take the example of fusing two remote cluster states together to form a larger, distributed virtual cluster. Imagine that their fusion operations are optically mediated by a satellite overhead. The options for satellite-mediated state fusion are (see Fig.~\ref{fig:sat_up_down}):
\begin{itemize}
	\item Downlink mode\index{Satellite downlink} --- The satellite uses the downlink to distribute an entangled Bell pair between the two nodes. Each node performs a Bell projection between their half of the Bell pair and their respective qubit from their local cluster state, thereby swapping the entanglement and creating a link. See Fig.~\ref{fig:sat_up_down}(a).
	\item Uplink mode\index{Satellite uplink} --- Each node takes an optical qubit from their cluster state (or entangles their cluster state qubit with an optical qubit), which is uplinked to the satellite. The satellite performs a Bell projection between the two received optical qubits, thereby implementing entanglement swapping between the two nodes, creating a link. See Fig.~\ref{fig:sat_up_down}(b).
\end{itemize}

\begin{figure*}[htpb]
	\includegraphics[width=\textwidth]{satellite_downlink_uplink}
	\caption{Satellite-mediated cluster state fusion operations for creating a link between two cluster states held by distant ground nodes. (a) Via entanglement distribution over a downlink channel. (b) Via distributed Bell projection over an uplink channel. When performing a distributed Bell measurement it is essential that the optical qubits arrive synchronously at the entangling measurement device, denoted \mbox{$\ket{\Psi^+}\bra{\Psi^+}$} (e.g a PBS), which is technologically challenging to implement on satellite given the unpredictable nature of the atmospheric quantum channel, necessitating on-board quantum memories to synchronise the qubits. This is likely to make (a) cheaper, faster and more efficient than (b).} \label{fig:sat_up_down}
\end{figure*}

@@

This yields several key advantages in favour of entanglement distribution as opposed to server-side joint entangling measurements:
\begin{enumerate}
	\item The challenging prospect of quantum memory may operate on Earth, far less onerous and expensive than incorporating this technology into a satellite in low-Earth orbit.
	\item Because the server is not storing any qubits in quantum memory, it does not suffer downtime associated with the periods between receiving the first photon and waiting for the second -- it can continue to spit out Bell pairs at maximum capacity.
	\item The satellite remains passive, implementing only the simplest of possible operations, reducing mass-production costs.
	\item The satellite does not require any interaction with its clients (classical or quantum).
	\item Because Bell pairs are known, infinitely reproducible states, the server can operate in a UDP-like\index{User Datagram Protocol (UDP)} mode and it is not problematic if any given pair was lost. In the reverse direction, loss of a qubit could compromise the entire peripheral state associated with it in the ground statio.
	\item Entanglement purification can be employed to enhance the effective quality of the transmission channel.x
\end{enumerate}

>>>>

Foremost, Bell pairs (Sec.~\ref{sec:bell_state_res}) -- the simplest entangled states -- are an utterly indispensable resource for countless quantum protocols. In brief, Bell pairs find applicability in, amongst many others, the following key protocols:
\begin{itemize}
\item Cluster states (Sec.~\ref{sec:CSQC})\index{Cluster states}: a Bell pair is also a 2-qubit cluster state, a supply of which can be employed in fusion strategies to prepare larger cluster states, enabling universal, distributed MBQC.
\item Quantum state teleportation (Sec.~\ref{sec:teleport})\index{Quantum state teleportation}: a shared Bell pair between Alice and Bob forms the elementary quantum resource upon which the state teleportation protocol is constructed.
\item QKD (Sec.~\ref{sec:QKD})\index{Quantum key distribution (QKD)}: the E91 QKD\index{E91 protocol} protocol is built upon a reliable stream of distributed Bell pairs, enabling private communication with perfect information theoretic security.
\item Modularised quantum computation (Sec.~\ref{sec:module})\index{Modularised quantum computation}: using Bell pairs, entanglement swapping (Sec.~\ref{sec:swapping})\index{Entanglement swapping} can be employed to fuse neighbouring, but potentially distant modules together using operations local to each module.
\item Superdense coding (Sec.~\ref{sec:superdense})\index{Superdense coding}: a shared Bell pair enables the communication of two classical bits of information via transmission of a single qubit, thereby doubling classical channel capacity\index{Channel capacity}.
\item Quantum-enabled telescopy (Sec.~\ref{sec:telescopy}): a shared Bell pair between two telescopes allows a photon received at one telescope to be teleported to the other, at which point interferometric techniques yield extremely sensitive phase information.
\end{itemize}

@@

So which ought our quantum hubs specialise in, entanglement distribution, entangling measurements, or both? For most practical purposes the former is far more powerful and robust. Let us take the example of fusing two remote cluster states together to form a larger, distributed virtual cluster. Imagine that their fusion operations are optically mediated by a satellite overhead. The options for satellite-mediated state fusion are (see Fig.~\ref{fig:sat_up_down}):
\begin{itemize}
	\item Downlink mode\index{Satellite downlink} --- The satellite uses the downlink to distribute an entangled Bell pair between the two nodes. Each node performs a Bell projection between their half of the Bell pair and their respective qubit from their local cluster state, thereby swapping the entanglement and creating a link.
	\item Uplink mode\index{Satellite uplink} --- Each node takes an optical qubit from their cluster state (or entangles their cluster state qubit with an optical qubit), which is uplinked to the satellite. The satellite performs a Bell projection between the two received optical qubits, thereby implementing entanglement swapping between the two nodes, creating a link.
\end{itemize}

\if 2\pubmode
	\begin{figure}[!htbp]
		\includegraphics[width=0.475\textwidth]{satellite_downlink_uplink_long}
		\caption{Satellite-mediated cluster state fusion operations for creating a link between two cluster states held by distant ground nodes. (top) Via entanglement distribution over a downlink channel. (bottom) Via distributed Bell projection over an uplink channel. When performing a distributed Bell measurement it is essential that the optical qubits arrive synchronously at the entangling measurement device, denoted \mbox{$\ket{\Psi^+}\bra{\Psi^+}$} (e.g a PBS), which is technologically challenging to implement on satellite given the unpredictable nature of the atmospheric quantum channel, necessitating on-board quantum memories to synchronise the qubits. This is likely to make downlinks cheaper, faster and more efficient than uplinks.} \label{fig:sat_up_down}
	\end{figure}
\else
	\begin{figure*}[!htbp]
		\includegraphics[width=\textwidth]{satellite_downlink_uplink}
		\caption{Satellite-mediated cluster state fusion operations for creating a link between two cluster states held by distant ground nodes. (left) Via entanglement distribution over a downlink channel. (right) Via distributed Bell projection over an uplink channel. When performing a distributed Bell measurement it is essential that the optical qubits arrive synchronously at the entangling measurement device, denoted \mbox{$\ket{\Psi^+}\bra{\Psi^+}$} (e.g a PBS), which is technologically challenging to implement on satellite given the unpredictable nature of the atmospheric quantum channel, necessitating on-board quantum memories to synchronise the qubits. This is likely to make downlinks cheaper, faster and more efficient than uplinks.} \label{fig:sat_up_down}
	\end{figure*}
\fi

@@

This yields several key advantages in favour of entanglement distribution as opposed to server-side joint entangling measurements:
\begin{enumerate}
	\item The challenging prospect of quantum memory may operate on Earth, far less onerous and expensive than incorporating this technology into a satellite in low-Earth orbit.
	\item Because the server is not storing any qubits in quantum memory, it does not suffer downtime associated with the periods between receiving the first photon and waiting for the second -- it can continue to spit out Bell pairs at maximum capacity.
	\item The satellite remains passive, implementing only the simplest of possible operations, reducing mass-production costs.
	\item The satellite does not require any interaction with its clients (classical or quantum).
	\item Because Bell pairs are known, infinitely reproducible states, the server can operate in a UDP-like\index{User Datagram Protocol (UDP)} mode and it is not problematic if any given pair was lost. In the reverse direction, loss of a qubit could compromise the entire peripheral state associated with it in the ground statio.
	\item Entanglement purification can be employed to enhance the effective quality of the transmission channel.
\end{enumerate}

### 2018-08-25 Sections/network_algorithms.tex
Added quantum voting, enigma machines
Started 2 col figs

\startnormtable
\begin{table*}[htpb]
	\begin{tabular}{|c|c|c|c|}
		\hline
  		\rowcolor{Dandelion} Algorithm & Description & Complexity class & Scaling \\
  		\hline
  		\hline
  		\rowcolor{LimeGreen} Breadth-first-search & Explore all vertices in a graph & \textbf{P} & $O(|V|+|E|)$ \\
  		\hline
  		\rowcolor{LimeGreen} Depth-first-search & (same as above) & \textbf{P} & $O(|V|+|E|)$ \\
		\hline
  		\rowcolor{LimeGreen} Shortest-path (Dijkstra) & Find the shortest route between two nodes & \textbf{P} & $O(|V|^2)$ \\
  		\rowcolor{LimeGreen} & in a directed graph & &  \\
  		  		\hline
		\rowcolor{LimeGreen} Shortest-path (\textit{A*}) & (same as above) & \textbf{P} & (varying) \\
  		  		\hline
		\rowcolor{LimeGreen} Single-source shortest path & Find the shortest paths from a given node to & \textbf{P} & $O(|V|\cdot |E|)$\\
  		\rowcolor{LimeGreen} & \textit{all} other nodes & & \\
 		\hline
		\rowcolor{LimeGreen} Minimum spanning tree & Find a spanning tree of a graph that minimises & \textbf{P} & $O(|E|\log |V|)$ \\
  		\rowcolor{LimeGreen} & the total of the edge weights & & \\
  		\hline
  		\rowcolor{LimeGreen} Minimum cost flow & Minimise total costs in a network &  \textbf{P} & $O(|V|\log |V|(|E|$\\
  		\rowcolor{LimeGreen} (Orlin) & with a specified amount of flow& & $+|V|\log |V|))$ \\
  		\hline
  		\rowcolor{LimeGreen} Maximum flow & Maximise flow in a network, regardless of costs & \textbf{P} & $O(|E|\cdot c_\mathrm{max})$ \\
  		\rowcolor{LimeGreen} (Ford-Fulkerson) & & & \\
  		\hline
  		\rowcolor{Lavender} Multi-commodity flow & Same as maximum flow, but generalised to & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & arbitrary numbers of users & (exactly), & \\
  		\rowcolor{Lavender} & & \textbf{P} (approximation & \\
  		\rowcolor{Lavender} & & using heuristics) & \\
  		\hline
  		\rowcolor{Lavender} Vehicle routing problem & Generalises the shortest-path algorithm to multiple & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & users, with distinct sources and destinations & & \\ 
  		\hline
  		\rowcolor{Lavender} Vehicle rescheduling problem & Same as above but with dynamically changing costs & \textbf{NP}-complete & ? \\
    	\hline
	\end{tabular}
	\caption{Summary of some important network algorithms and their complexities. The \textbf{NP}-complete algorithms are not believed to have efficient classical algorithms, and their exact scaling is not well understood.} \label{tab:net_alg_sum} \index{Network algorithms}\index{Breadth-first-search (BFS) algorithm}\index{Depth-first-search (DFS) algorithm}\index{Shortest-path algorithm}\index{Single-source shortest path algorithm}\index{Minimum spanning tree algorithm}\index{Minimum cost flow algorithm}\index{Maximum flow algorithm}\index{Multi-commodity flow algorithm}\index{Vehicle routing problem}\index{Vehicle rescheduling problem}
\end{table*}
\startalgtable

@@

\begin{figure}[htpb]
\includegraphics[width=0.3\textwidth]{BFS_DFS}
\caption{Comparison of the order in which vertices are explored, using the breadth-first-search (BFS) and depth-first-search (DFS) algorithms, where vertex 1 is the root vertex.} \label{fig:BFS_DFS}
\end{figure}

@@

The first proven shortest-path algorithm was by Dijkstra \cite{bib:Dijkstra59}, which requires runtime,
\begin{align}
	O(|V|^2),
\end{align}
also residing in \textbf{P}\index{P}. Subsequently, a number of improvements and variations on Dijkstra's algorithm have been proposed, most notably the $A^*$ algorithm \cite{bib:Astar}\index{Shortest-path algorithm}, which has found widespread modern use, using a heuristic approach to improve performance over Dijkstra.

@@

\begin{table}[htpb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function DijkstraShortestPath($G$,$A$,$B$):
\begin{enumerate}
	\item currentNode = $A$
    \item tentativeDistances[$A$] = 0
    \item tentativeDistances[others] = $\infty$
    \item nodesVisited[$A$] = True
    \item nodesVisited[others] = False
    \item loopStart:
    \item neighbours = currentNode.neighbourhood
    \item nodesVisited[neighbours] = True
    \item for(n$\in$neighbours) \{
    \setlength{\itemindent}{0.2in}
    \item newTentativeDist = \\ min(tentativeDistances[currentNode] \\+ edgeWeight[currentNode,n],\\
        tentativeDistances[n])\\
    \item nodesVisited[currentNode] = True
    \setlength{\itemindent}{0in}
    \item \}
    \item if(nodesVisited[$B$] = True) \{
    \setlength{\itemindent}{0.2in}
	\item return(tentativeDistances[$B$])
	\item $\Box$
    \setlength{\itemindent}{0in}
    \item \}
	\item currentNode = \\
	tentativeDistances[unvisitedNodes].\\
	nodeWithSmallest()
	\item goto(loop)
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\caption{Dijkstra's original shortest-path algorithm for finding the lowest weight path through a graph, $G$, between two vertices, $A$ (source) and $B$ (destination). The algorithm has $O(|V|^2)$ runtime (in \textbf{P}).} \label{alg:dijkstra}\index{Shortest-path algorithm}
\end{table}

>>>>

\startnormtable
\begin{table*}[!htbp]
	\begin{tabular}{|c|c|c|c|}
		\hline
  		\rowcolor{Dandelion} Algorithm & Description & Complexity class & Scaling \\
  		\hline
  		\hline
  		\rowcolor{LimeGreen} Breadth-first-search & Explore all vertices in a graph & \textbf{P} & $O(|V|+|E|)$ \\
  		\hline
  		\rowcolor{LimeGreen} Depth-first-search & (same as above) & \textbf{P} & $O(|V|+|E|)$ \\
		\hline
  		\rowcolor{LimeGreen} Shortest-path (Dijkstra) & Find the shortest route between two nodes & \textbf{P} & $O(|V|^2)$ \\
  		\rowcolor{LimeGreen} & in a directed graph & &  \\
  		  		\hline
		\rowcolor{LimeGreen} Shortest-path (\textit{A*}) & (same as above) & \textbf{P} & (varying) \\
  		  		\hline
		\rowcolor{LimeGreen} Single-source shortest path & Find the shortest paths from a given node to & \textbf{P} & $O(|V|\cdot |E|)$\\
  		\rowcolor{LimeGreen} & \textit{all} other nodes & & \\
 		\hline
		\rowcolor{LimeGreen} Minimum spanning tree & Find a spanning tree of a graph that minimises & \textbf{P} & $O(|E|\log |V|)$ \\
  		\rowcolor{LimeGreen} & the total of the edge weights & & \\
  		\hline
  		\rowcolor{LimeGreen} Minimum cost flow & Minimise total costs in a network &  \textbf{P} & $O(|V|\log |V|(|E|$\\
  		\rowcolor{LimeGreen} (Orlin) & with a specified amount of flow& & $+|V|\log |V|))$ \\
  		\hline
  		\rowcolor{LimeGreen} Maximum flow & Maximise flow in a network, regardless of costs & \textbf{P} & $O(|E|\cdot c_\mathrm{max})$ \\
  		\rowcolor{LimeGreen} (Ford-Fulkerson) & & & \\
  		\hline
  		\rowcolor{Lavender} Multi-commodity flow & Same as maximum flow, but generalised to & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & arbitrary numbers of users & (exactly), & \\
  		\rowcolor{Lavender} & & \textbf{P} (approximation & \\
  		\rowcolor{Lavender} & & using heuristics) & \\
  		\hline
  		\rowcolor{Lavender} Vehicle routing problem & Generalises the shortest-path algorithm to multiple & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & users, with distinct sources and destinations & & \\ 
  		\hline
  		\rowcolor{Lavender} Vehicle rescheduling problem & Same as above but with dynamically changing costs & \textbf{NP}-complete & ? \\
    	\hline
	\end{tabular}
	\caption{Summary of some important network algorithms and their complexities. The \textbf{NP}-complete algorithms are not believed to have efficient classical algorithms, and their exact scaling is not well understood.} \label{tab:net_alg_sum} \index{Network algorithms}\index{Breadth-first-search (BFS) algorithm}\index{Depth-first-search (DFS) algorithm}\index{Shortest-path algorithm}\index{Single-source shortest path algorithm}\index{Minimum spanning tree algorithm}\index{Minimum cost flow algorithm}\index{Maximum flow algorithm}\index{Multi-commodity flow algorithm}\index{Vehicle routing problem}\index{Vehicle rescheduling problem}
\end{table*}
\startalgtable

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[width=0.3\textwidth]{BFS_DFS_long}
	\caption{Comparison of the order in which vertices are explored, using the breadth-first-search (BFS) and depth-first-search (DFS) algorithms, where vertex 1 is the root vertex.} \label{fig:BFS_DFS}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[width=0.65\textwidth]{BFS_DFS}
	\caption{Comparison of the order in which vertices are explored, using the breadth-first-search (BFS) and depth-first-search (DFS) algorithms, where vertex 1 is the root vertex.} \label{fig:BFS_DFS}
	\end{figure*}
\fi

@@

The first proven shortest-path algorithm was invented by and named after Dijkstra \cite{bib:Dijkstra59}, which requires runtime,
\begin{align}
	O(|V|^2),
\end{align}
also residing in \textbf{P}\index{P} (one of the relatively few, and highly valuable optimisation problems that is classically efficient). Subsequently, a number of improvements and variations on Dijkstra's algorithm have been proposed, most notably the $A^*$ algorithm \cite{bib:Astar}\index{Shortest-path algorithm}, which has found widespread modern use, using a heuristic approach to improve performance over Dijkstra.

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function DijkstraShortestPath($G$,$A$,$B$):
\begin{enumerate}
	\item currentNode = $A$
    \item tentativeDistances[$A$] = 0
    \item tentativeDistances[others] = $\infty$
    \item nodesVisited[$A$] = True
    \item nodesVisited[others] = False
    \item loopStart:
    \item neighbours = currentNode.neighbourhood
    \item nodesVisited[neighbours] = True
    \item for(n$\in$neighbours) \{
    \setlength{\itemindent}{0.2in}
    \item newTentativeDist = \\ min(tentativeDistances[currentNode] \\+ edgeWeight[currentNode,n],\\
        tentativeDistances[n])\\
    \item nodesVisited[currentNode] = True
    \setlength{\itemindent}{0in}
    \item \}
    \item if(nodesVisited[$B$] = True) \{
    \setlength{\itemindent}{0.2in}
	\item return(tentativeDistances[$B$])
	\item $\Box$
    \setlength{\itemindent}{0in}
    \item \}
	\item currentNode = \\
	tentativeDistances[unvisitedNodes].\\
	nodeWithSmallest()
	\item goto(loop)
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\caption{Dijkstra's original shortest-path algorithm for finding the lowest weight path through a graph, $G$, between two vertices, $A$ (source) and $B$ (destination). The algorithm has $O(|V|^2)$ runtime (in \textbf{P}).} \label{alg:dijkstra}\index{Shortest-path algorithm}
\end{table}
